Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}

### 2020-02-07 response_to_reviewers.tex

\documentclass[11pt,a4paper]{letter}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage[dvipsnames,usenames]{color}
\usepackage{listings}
\usepackage{verbatim}

\geometry{verbose,letterpaper,tmargin=1in,bmargin=2in,lmargin=1in,rmargin=1in}
%\lstdefinestyle{lat}
%{
%	style={[LaTeX]TeX},
%	basicstyle=\ttfamily
%}

\newcommand{\red}[1]{\textbf{\textcolor{Red}{#1}}}
\newcommand{\blue}[1]{\textbf{\textcolor{Blue}{#1}}}
\newcommand{\cyan}[1]{\textbf{\textcolor{Cyan}{#1}}}
\newcommand{\green}[1]{\textbf{\textcolor{Green}{#1}}}
\newcommand{\magenta}[1]{\textbf{\textcolor{Magenta}{#1}}}
\newcommand{\orange}[1]{\textbf{\textcolor{Orange}{#1}}}
%\newcommand{\red}[1]{#1}
%\newcommand{\blue}[1]{#1}
%\newcommand{\cyan}[1]{#1}

% comments between authors
\newcommand{\toall}[1]{\textbf{\orange{@@@ To all: #1 @@@}}}
\newcommand{\towenjie}[1]{\textbf{\red{*** Wenjie: #1 ***}}}
\newcommand{\tojeroen}[1]{\textbf{\green{*** Jeroen: #1 ***}}}
\newcommand{\toebru}[1]{\textbf{\cyan{*** Ebru: #1 ***}}}
\newcommand{\fromebru}[1]{\textbf{\orange{*** Ebru: #1 ***}}}
\newcommand{\fromyouyi}[1]{\textbf{\blue{*** Youyi: #1 ***}}}

\newlength{\tempheight}
\newlength{\tempwidth}

\newcommand{\rowname}[1]% #1 = text
{\rotatebox{90}{\makebox[\tempheight][c]{\textbf{#1}}}}

\newcommand{\columnname}[1]% #1 = text
{\makebox[\tempwidth][c]{\textbf{#1}}}

%\graphicspath{{./figure/}}

\def\baselinestretch{2}
\newcommand{\response}[1]{\textbf{Response:} #1}

\newcommand{\rev}[1]{{\it{#1}}}

\newcommand{\tsup}[1]{\textsuperscript{#1}}

%\address{your name and address} 
\signature{Wenjie Lei, et al.}

\begin{document}

\begin{letter}{Dr.~Ivan Vasconcelos\\
Editor, \textit{Geophysical Journal International}}

\opening{Dear Dr.~Vasconcelos,}

This is our response to the reviews of \textit{Geophysical Journal International\/} manuscript GJI-19-0247 entitled ``Global Adjoint Tomography -- Model GLAD-M25''.
We received three reviews of our paper: one was basically favorable and involved a ``light'' revision, a second (by Ritsema) was critical but constructive, suggesting helpful major revisions, and a third was unprofessional and inappropriate, especially in view of the fact the the first author of the article is a graduate student.

The three main issues raised in the reviews and editorial comments are: 1) uncertainty quantification, 2) model interpretation, and 3) manuscript structure.
We have revised the manuscript accordingly,
and moved significant portions of the original manuscript to Supplementary Online Material (SOM).

What follows is a detailed point-by-point response to the reviewer's and editor's comments.
Reviewer/editor's comments are in italics verbatim, and our response is in normal type. The citations and section number in our response refer to the revised manuscript unless we specify otherwise.

{\textbf{\large Response to Editor Vasconcelos}}

\rev{On technical advancement: the authors have made significant technical advances, as recognized by all three referees, however, the referees point out several technical points that could be better addressed (e.g., uncertainty analysis) in order to provide the credibility that the advances presented in this manuscript deserve. I leave it to the authors to decided how to address these points, e.g., either by restructuring the paper, incorporating additional studies/examples, or both.
}

\response{Uncertainty quantification is a long-standing challenge in seismic tomography that dates back to its inception. Checkerboard tests are basically useless (e.g., L\'ev\^eque, Rivera, and Wittlinger, 1993), and even ``proper'' tools, such as the resolution matrix suffer from the fact that ``resolution'' is controlled by playing with a subjective damping parameter. Bayesian
 inference would be a preferred method of inversion, but this is obviously not an option for the current study; an unavoidable fact that even Albert Tarantola grudgingly accepted.
Ideally, we would have tools that enable us to take multiple samples from the posterior model distribution, but unfortunately such tools have thus far eluded the community.
This is the reality in which the current study was conducted.

In this context we have tried, more so than other studies, to assess the quality of our model.
First, we calculate variance reductions for more than 20 million time windows and demonstrate quantitatively that M25 provides a significantly better fit to the data than both M15 and S362ANI.
We note at this point that ISC traveltime inversions often provide less than 10\% reductions in variance to \emph{only} P and S wave traveltimes (Nolet, personal communication).
Second, we present traveltime histograms for three-component measurements in four different passbands, and we demonstrate that the mean and standard deviations for model M25 are consistently reduced relative to M15 and S362ANI.
Finally, we use a held-out dataset of 320 earthquakes to demonstrate that these events, which were not used in the inversion, are fit equally well as the 1,480 events in the actual dataset (Incidentally, in this context, we find the comment by reviewer 2 that our paper lacks ``true scientific innovation'' insulting).
The original manuscript did not contain point-spread function (PSF) tests,
but several such tests are included in the revived manuscript.
A PSF does not say much about uncertainty ---like checkerboard tests and the resolution matrix--- but gives an idea of resolution and model parameter tradeoffs.
}

\rev{On interpretation of the results: the reviewers commend the technical achievements of the authors, but are simply not convinced that the model obtained is a sufficient advancement on the authors previous model, in terms of providing new insight into Earth structure and/or composition.
Because this is a significant component of the current manuscript, the authors must decide how to best address these concerns: either by better supporting their interpretation with additional evidence (related to the previous point), or by choosing to write a new version that focuses on methodological tomography advances, and not so much on interpretation just yet (as suggested by reviewers).
}

\response{To say that the new model, GLAD-M25, is not a significant advancement over the previous model, GLAD-M15, is perplexing. First, we provide quantitative evidence in the forms of misfit reductions (Tables 1 \& 2) and traveltime \& amplitude histograms (Figs.~10, 11, 12, 14 \& 15 in the original manuscript) that M25 fits the data better than M15.
Second, M25 resolves numerous new features that were entirely missing in M15, such as the Fiji-Tonga slab near New Zealand, and various hotspots in the Indian Ocean.
Rather than focusing on comparisons between M15 and M25, we chose to show comparisons with several global and regional models.
In response to the reviews,
we have reduced the number of model comparisons, focusing on plumes and subduction zones instead.
}

\rev{On manuscript structure and language: as pointed out by reviewers, this papers overall structure is indeed very similar to that of the Bozdag et al. (2016, GJI) one; it is by no means a copy-paste in content (this is a 'new' manuscript), but the structural similarity is there. In addition, reviewers and myself feel that the language used, particularly in the interpretation sections, is indeed a bit 'grandiose': while it is important to clearly highlight important points, there is also a danger of coming across as 'overselling'. As Editor, I personally would prefer if, in their new version, the authors would: i) reconsider the design/structure of the manuscript as to not be so similar to previous publications, ii) consider the language used in discussing results to indeed positively promote their advancements, while maintaining a critical, tempered tone. Please note this last point is 'Editorial preference', where the authors can improve delivery: while the two points above are the criteria used in my recommendation, this point is intended as an 'easy to implement' improvement.
}

\response{The present study involves a 6-fold increase in the number of earthquakes compared to M15 (1,480 events versus 253 events), but it uses the same model parameterization and has the same goal of constraining global mantle structure.
To enable the scale-up in the number of events, substantial advances were made in the development of the workflow management tools.
Rather than belaboring this work, we have moved much of this discussion to the SOM.
We have also taken suggestions to tone down the language to heart.
}

{\textbf{\large{Response to Reviewer~1}}}

\rev{In the introduction and conclusion it is mentioned that attenuation is fully accommodated in calculations.
I understand why the authors claim this, but nowhere is mentioned which attenuation model is used. I presume PREM, which we know is way off.
Is their model affected by this choice?
It is one thing dealing approximately with a bad model, it is another dealing exactly with a bad model.
}

\response{The 1D model is QL6~(Durek \& Ekstr\"om, 1996), which is also not ideal, but there are not really any better options,
and this is one of the main reasons why we are using phase information only.
However,
of course the reviewer is correct that any inversion is affected by the choice of and uncertainties in the attenuation model. 
This issue will be the subject of future studies.
}

\rev{In the relocation of the 1040 earthquakes, they allow for an arbitrary time shift of the synthetics. What is the justification of this and how big is this $\Delta t$.
I  think this needs explaining as later they add another 440 events without relocation and therefore no such time shift.
Is there not a risk that the centroid times of their whole dataset is now biased?
}

\response{The time shift parameter in the CMT inversion algorithm developed by~Liu et al.~(2004) accommodates structural uncertainty and has nothing to do with the centroid time.
It provides a means of estimating source parameters while minimizing contamination by lateral heterogeneity.
Note, however, that as part of every iteration we perform a grid search for the scalar moment and centroid time in the current 3D model,
and these corrections contribute to the final CMT solution.
The fact that the traveltime histograms are reasonably well centered
on zero suggests that there is no systematic bias in the centroid times.
}

\rev{They claim that the choice of the misfit function is important. I agree of course, but the reader only sees equations for the weights they use (eqs. 5 and 6). Is there a way to visualize these and what are their effects on the model.
}

\response{Yes, this is the subject of the Ruan et al.~(2019) paper, and we did not want to reproduce the related figures.}

\rev{In the model parametrization, they go from 5 Love parameters to 4 wave speeds. They   go from 5 to 4 parameters not because the introduce bulk sound speed, but because they explicitly assume A=C I presume.
}

\response{No, we assume $A=\kappa+\tfrac{4}{3}\,N$ and $C=\kappa+\tfrac{4}{3}\,L$\,. Thus the P wave anisotropy comes via the shear moduli.}

\rev{I wonder what window sorting and cleaning entails. How many outliers are eliminated?
}

\response{After plotting traveltime histograms towards the end of the window selection process, we clip the tails of the distribution, eliminating ~$3\sigma$~outliers.
This entails just a handful of ~$3\sigma$~outliers that may contaminate the model update.
}

\rev{They smooth the gradient differently to what they did in their previous 15 iterations. Has this a large effect? Obviously they must have a reason for changing this based on some tests.
}

\response{We changed the weighting scheme for sources and receivers,
which eliminates the need for the previously used variable smoothing of the gradient.
The weighting strategy is discussed in detail in~Ruan et al.~(2019), and includes examples of improved convergence.
One may still use multi-scale smoothing with the new weighting scheme to allow for smaller-scale heterogeneities under densely sampled regions.
}

\rev{Concerning the model evaluation, they refrained from point spread functions. Instead they show detailed misfits and comparisons with other published models.
I can understand that PSFs are computationally expensive (by the way they could reference the authors who suggested them first for FWI), but they are the only objective way to assess resolution.
Comparisons with existing models are not very helpful if these models have been done with different theories, data etc.
I would suggest at least to make a detailed comparison with GLAD-M15. Do we get visually a better resolution by throwing that much more data and GPU time at the problem. I suspect yes, but I still would like to see what improves where. 
}

\response{We provide detailed comparisons between M15 and M25 in Tables~1 and~2, as well as in all the traveltime and amplitude histograms.
In the revised manuscript we have also added a couple of new figures directly comparing M15 and M25, thereby highlighting distinct new features in M25.}

\rev{The authors mention that checkerboards are expensive. One could also mention that in fact they are useless for assessing resolution.
}

\response{Indeed. See our earlier discussion.}

\rev{The authors mention that the perturbations tend to be larger than in other models. I fully understand why this is, but it has a huge consequence for the interpretation of the model. We are now moving away from perturbations and enter the domain of finite difference. Trying to understand these models with partial derivatives for temperature and composition will be very misleading. If we want to infer temperature and composition, we will have to work with absolute values.
}

\response{That's correct. This is why we would prefer to share our model in the form of absolute values of wavespeeds.
Perturbations are desirable to show vertical sections, or at least the mean should be removed.
}

\rev{In that respect, I find the plume pictures for instance over-interpreted. What tells us that red in the upper mantle means the same as red at the CMB.
If they are confident that it means the same, they can say, for instance, the Iceland plume rises from the CMB, if not, it will be a different story.
The same holds for slabs. I suggest to be a bit more careful than just falling in the old habit that red is hot and blue is cold. The deviations are now so large that these analogies become misleading.
}

\response{We have modified the language.}

\rev{They don't mention anisotropy, but clearly invert for TI as claimed in the technical section. Do they see any evidence of anisotropy in the lower mantle for instance?
}

\response{As in M15, transverse isotropy in M25 is confined to the upper mantle, because it is mainly constrained by surface waves. }

{\textbf{\large{Response to Reviewer~2}}}

\rev{The authors describe a global waveform inversion based on spectral-element simulations and adjoint techniques. The outline follows numerous previous publication of roughly the same group of authors: presentation of the initial model, the distribution of events, of data and measurements, model parametrization, workflow, misfit evolution, and the final model.

I am fully aware that such an inversion is technologically challenging, and that the authors aim to publish the current state of their model. However, I have some rather serious and fundamental concerns that I would like to see addressed before making any more detailed comments. Specifically, I have difficulties to discover any true scientific innovation. To me, adding some events and slightly reducing the minimum period is clearly too incremental. If our community were to operate in such a mode, we would see a flood of tomographic models, each being an update of its predecessor with a few more iterations. This would slow down progress instead of accelerating it. Furthermore, the absence of even the slightest effort to assess the resolution of the model is hardly acceptable. Of course, nobody would request that the full resolution operator be computed for such an inversion, but some reasonable effort must be made. Simply writing that you ran out of computational resources to check the quality of the model is rather dubious.

As I wrote before, I perfectly know that this inversion is not a trivial task, and I do believe that it should be published somewhere. However, I really do not think that GJI is a suitable journal for this manuscript. My suggestion would be to refocus the manuscript on the technical and computational aspects, and to send it to a computational science journal.
}

\response{We appreciate the scientific criticisms of the reviewer.
We believe that both technically and scientifically our community will benefit from our efforts and experiences, because this is the first time this volume of data is
assimilated in such a computationally large-scale global inversion.
Therefore,
we believe that GJI is the right journal for this manuscript,
especially in view of the fact that many other papers on earthquake FWI/adjoint tomography have been published in GJI.
We do not agree with the reviewer that the slight reduction in minimum period is too incremental, and should thus not be considered scientific progress.
In fact, even though the period range of GLAD-M25 is similar to that of GLAD-M15,
we observe significant differences between the two models,
thanks to the 6-fold increase in the number of earthquakes,
including more than 500 deep events with very clean body waves.
Belittling our work with comments like ``adding some events'' when scaling the inversion up from 253 events to 1,480 events involved a herculean effort, especially on behalf of the first-author graduate student, is totally unprofessional and completely uncalled for.

We naively assumed that it was obvious from the GLAD-M15 GJI article and the histograms and comparisons with other models in this manuscript.
However, based on the comments of all the reviewers we now directly compare GLAD-M15 and GLAD-M25 in the revised manuscript,
thereby highlighting visual differences between the models, in addition to the the tables with variance reductions and traveltime and amplitude anomaly histograms.

There is still a vast amount of information to be explained in seismograms at the global scale, which requires more iterations and, probably, a more complete parameterization.
However, the reviewer is missing the main point --- or, more likely, we did not explain it well --- which is that we decided to publish GLAD-M25 because its resolution (scale-length of heterogeneities) has become comparable to the current resolution of global models from various other groups.
Thus we did not arbitrarily decide to publish this model,
and we certainly do not advocate publishing every iteration as a new model.
%We now highlight it in the manuscript that the vast amount of remaining data in the seismograms should continue changing the models which also points out the necessity of our non-linear iterative inversions.

Finally, resolution and uncertainty quantification remain a challenge in FWI,
both in exploration and earthquake seismology.
In lieu of such tools,
as in numerous other studies,
we used traveltime histograms and a held-out dataset to assess performance of our model.
We did not perform PSF tests, because these are rather limited in value, especially in view of the fact that they only tell you something about one ``point'' in the model for the set up of a particular iteration.
Therefore, a PSF does not say much about uncertainty, but gives an idea of resolution.
Nevertheless,
as mentioned earlier,
the updated manuscript now contains a few PSF tests.}

\rev{(1) By far my biggest concern is the lack of true scientific innovation. While the authors do mention some recent technological improvements (e.g., the storage algorithm for anelastic kernels and the ASDF data format), all of them have been published before, and are therefore not new. Apart from adding more events and going to slightly higher frequencies, this work is very similar to the previously published work by Bozdag et al. (2016). Also, the final model does not reveal anything about the structure of the Earth that was not known before.
}

\response{The main technical improvement is the workflow management.}

\rev{(2) In section 9.1, entitled "Point-spread function analysis", the authors explain that they actually did not perform such tests because they are computationally too expensive. Instead, they refer to 2 previous point-spread function calculations, published by Bozdag et al. (2016), using the earlier dataset.

Risking that I may sound unprofessional and harsh, I am sorry to say that this is ridiculous!

First of all, if one runs out of computational resources needed to check the quality of a model, it simply means that the inversion has been poorly planned! I am sure the authors know the number of node hours per forward run very well. It is therefore simply a matter of choosing a minimum period that leaves enough resources to run a reasonable model assessment. Simply saying that you better like to use the INCITE resources to just produce a colorful model, is a miserable excuse that I find completely unacceptable.

Second, it is not clear what to learn from 2 point-spread functions (apart from the fact that they were computed for different data). As the authors demonstrate in section 10 of their manuscript (interpretation and comparison), there are many more than 2 interesting points inside the Earth.

Third, the authors dedicate 13 pages (!!!) to the comparison of their new model to the previous and to other models. However, without any quantitative information on how much the new model has improved, this seems to be a rather meaningless exercise.
}

### 2020-02-07 main.tex
update
Updates from Overleaf

@@

\author[Lei et al.]
  {Wenjie Lei$^1$, Youyi Ruan$^{1,2}$, Ebru Bozda\u g$^3$, Daniel Peter$^4$, Matthieu Lefebvre$^1$, \\{\LARGE \rm Dimitri Komatitsch$^5$, Jeroen Tromp$^{1,6}$, Judith Hill$^7$, Norbert Podhorszki$^7$}, \\ {\LARGE \rm and David Pugmire$^7$} \\
  $^1$ Department of Geosciences, Princeton University, Princeton, NJ 08544, USA\\
  $^2$ School of Earth Sciences and Engineering, Nanjing University, Nanjing, Jiangsu 210023, China\\
  $^3$ Department of Geophysics, Colorado School of Mines, Golden, CO 80401, USA\\
  $^4$ Extreme Computing Research Center, King Abdullah University of Science and Technology (KAUST), \\Thuwal 23955-6900, Kingdom of Saudi Arabia\\
  $^5$ LMA, CNRS UPR 7051, Aix-Marseille University, Centrale Marseille, 13453 Marseille Cedex 13, France\\
  $^6$ Program in Applied and Computational Mathematics, Princeton University, Princeton, NJ 08544, USA\\
  $^7$ Oak Ridge National Laboratory, Oak Ridge, TN 37831, USA\\
  }

@@

%%---------------------------------------------
%
%   Summary
%
%%---------------------------------------------
\begin{summary}
Building on our first-generation global adjoint tomography model,
GLAD-M15~\citep{bozdaug2016global}, we present our second-generation transversely isotropic global model,
named GLAD-M25, which is the result of ten quasi-Newton tomographic iterations with an
earthquake database consisting of 1,480 events in the magnitude range $5.5\le M_w \le 7.2$,
an almost six-fold increase over the first-generation model.
We calculated fully 3D synthetic seismograms with a shortest period of 17~s based on a GPU-accelerated spectral-element wave
propagation solver which accommodates effects due to 3-D anelastic crust \& mantle structure, topography \& bathymetry, the ocean load, ellipticity, rotation, and self-gravitation.
We used an adjoint-state method to calculate Fr\'echet derivatives in 3D anelastic Earth models
facilitated by a parsimonious storage algorithm.
The simulations were performed on the Cray XK7 ``Titan'' at the Oak Ridge Leadership Computing Facility.
We quantitatively evaluated GLAD-M25 by assessing misfit reductions and traveltime \& amplitude anomaly histograms in twelve measurement
categories.
We performed similar assessments for a held-out data set consisting of 360 earthquakes,
with results comparable to the actual inversion.
We compare GLAD-M25 with numerous other global and regional models,
and highlight a variety of plumes and subduction zones.
\end{summary}

@@

Current global seismic models are in general agreement regardless of data type and inversion strategy in terms of long-wavelength heterogeneity \citep{ritzwollerlavely1995,TW01,beckerboschi2002}.
However, discrepancies between models become noticeable as resolution increases.
Using accurate 3D simulations of seismic wave propagation and the computation of data sensitivities in 3D background models are key requirements for improving resolution in tomographic images on all scales.
Such detailed images are essential for understanding mantle dynamics and related surface tectonic processes
---for example the origin of hotspots and the forces behind plate motions and earthquakes.
Higher resolution wavespeed models are also important for accurately locating earthquakes, and are required from an engineering point of view to assess seismic hazard in earthquake prone regions and to detect nuclear explosions.

With these goals in mind,
in this study we use a GPU-accelerated version of the 3D spectral-element solver
SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b} on the Cray supercomputer ``Titan'' at the Oak Ridge Leadership Computing Facility (OLCF) for global adjoint tomography.
These simulations accommodate the full 3D complexity of global Earth models,
including 3D anelastic crust and mantle structure, self-gravitation, rotation, ellipticity, topography \& bathymetry, and the load of the oceans.
No compromises are made with regards to resolving the Earth's crust,
which is explicitly captured by the spectral-element mesh~\citep{tromp2010a},
thereby eschewing the need for ubiquitous ``crustal corrections''.
The ultimate goal is to use every single piece of information in seismograms,
a task made partly feasible based on the automated window selection tool FLEXWIN~\citep{maggi2009automated}.

Global adjoint tomography has a well-defined but complex workflow with multiple stages.
% including numerical simulations of synthetic seismograms (forward simulations) for all events,
% pre-processing of seismic data, making measurements, data assimilation, Fr\'echet derivative
% calculations (adjoint simulations), and post-processing of the gradient for quasi-Newton model
% updates.
It is essential to optimize, automate, and harden the entire process using workflow management tools, especially with large data sets.
For each iteration,
1,480 forward and adjoint simulations need to be performed,
generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours.
How to deal with hardware failures during this process is critical
to prevent contamination of the inversion results.
For these reasons, we use EnTK as our
workflow management engine~\citep{EnTK2017}.
This workflow engine can automatically detected job failures,
both from the high-performance computing (HPC) system and via user-defined functions.
This facilitates tracking of tasks and semi-automatic job resubmission if necessary.

In this article we compare the results of our inversion with a number of previous tomographic models.
On a global scale, we present comparisons with model S362ANI$+$M~\citep{moulik2014anisotropic},
which is an updated version of model S362ANI~\citep{kustowski2008anisotropic},
the starting model for the GLAD-M15 inversion.
We also consider global shear wavespeed models S40RTS~\citep{ritsema2011s40rts},
TX2015~\citep{TX2015}, SEMUCB-WM1~\citep{french2015broad},
and SL2013sv~\citep{SchaefferLebedev13},
as well as compressional wavespeed models LLNL-G3Dv3 \citep{simmons2012llnl}, GAP-P4~\citep{fukao2013subducted}, and UU-P07~\citep{van2018atlas}.
On the scale of North America
we make comparisons with models US22~\citep{zhu2017radial},
a radially anisotropic model based on adjoint tomography using USArray data from 180 regional earthquakes,
and SL2013NA~\citep{schaeffer2014imaging},
a modification of global model SL2013sv focused on North America.
In Europe we use regional model EU60~\citep{zhu2015seismic} for comparison,
which is based on the assimilation of data from 190 regional earthquakes recorded by more than 700 European seismographic stations.
Finally, in Asia we use regional adjoint tomography model EARA2014~\citep{chen2015multiparameter} as a reference, a model based on data from 227~earthquakes recorded by more than 1,800~stations.

This article is organized as follows.
Sections~\ref{section:start}--\ref{section:data} describe the starting model,
earthquake database, and seismographic data set. 
Sections~\ref{section:misfit} and~\ref{section:parameterization} describe the misfit function minimized during the inversion process
and the related model parameterization.
In Section~\ref{section:workflow} we describe the adjoint tomography workflow in some detail.
Section~\ref{section:misfit_evolution} describes the evolution of the misfit, and in Section~\ref{section:evaluation} we evaluate the model based on a held-out data set of 360 earthquakes.
Finally, in Section~\ref{section:model}, we describe the model in detail,
offering many comparisons with various global and regional models, as described in the proceeding paragraph.
We conclude with a discussion of future opportunities and directions.

\section{Starting model GLAD-M15}
\label{section:start}

As a continuation of our previous work~\citep{bozdaug2016global},
we used the first-generation model GLAD-M15 as our
starting model.
GLAD-M15 is a 3D transversely isotropic earth earth model, which combined
3D mantle model S362ANI~\citep{kustowski2008anisotropic}
with 3D crustal model CRUST2.0~\citep{bassin2000current} as its starting model.
In this study,
we continue to use the same transversely isotropic model parametrization.
Instead of relying on crustal corrections,
the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us to accurately accommodate topography and bathymetry as well as variations in the Moho.
GLAD-M15 was constructed using a global database of 253 earthquakes.
The first 12 iterations of the GLAD-M15 inversion used three-component seismograms with a shortest period of 27~s,
and the final 3 iterations reduced this further to 17~s.
In this study we also used three-component seismograms with a shortest period of 17~s.

\section{Earthquakes}
\label{section:earthquakes}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
  \caption{\small{Source corrections for 1,040 out of 1,480 events used in the structural inversion. (a) Map view of depth changes. (b) Distribution of seismographic stations used for source inversions. (c) Depth change relative to the original global CMT Catalog depth. (d)--(f) Histograms of depth, origin time, and scalar moment changes relative to the CMT Catalog.
  }}
  \label{fig:source_correction}
\end{figure}

>>>>

% comments between authors
\newcommand{\toall}[1]{\textbf{\orange{@@@ To all: #1 @@@}}}
\newcommand{\towenjie}[1]{\textbf{\red{*** Wenjie: #1 ***}}}
\newcommand{\tojeroen}[1]{\textbf{\green{*** Jeroen: #1 ***}}}

@@

\author[Lei et al.]
  {Wenjie Lei$^1$, Youyi Ruan$^{1,2}$, Ebru Bozda\u g$^3$, Daniel Peter$^4$, Matthieu Lefebvre$^1$, \\{\LARGE \rm Dimitri Komatitsch$^5$, Jeroen Tromp$^{1,6}$, Judith Hill$^7$, Norbert Podhorszki$^7$}, \\ {\LARGE \rm and David Pugmire$^7$} \\
  $^1$ Department of Geosciences, Princeton University, Princeton, NJ 08544, USA\\
  $^2$ School of Earth Sciences and Engineering, Nanjing University, Nanjing, Jiangsu 210023, China\\
  $^3$ Department of Geophysics, Colorado School of Mines, Golden, CO 80401, USA\\
  $^4$ Extreme Computing Research Center, King Abdullah University of Science and Technology (KAUST), \\Thuwal 23955-6900, Kingdom of Saudi Arabia\\
  $^5$ LMA, CNRS UPR 7051, Aix-Marseille University, Centrale Marseille, 13453 Marseille Cedex 13, France\\
  $^6$ Program in Applied and Computational Mathematics, Princeton University, Princeton, NJ 08544, USA\\
  $^7$ Oak Ridge National Laboratory, Oak Ridge, TN 37831, USA
  }

@@

%%---------------------------------------------
%
%   Summary
%
%%---------------------------------------------
\begin{summary}
Building on global adjoint tomography model~GLAD-M15~\citep{bozdaug2016global}, we present transversely isotropic global model~GLAD-M25,
which is the result of ten quasi-Newton tomographic iterations with an
earthquake database consisting of 1,480 events in the magnitude range $5.5\le M_w \le 7.2$,
an almost six-fold increase over the first-generation model.
We calculated fully 3D synthetic seismograms with a shortest period of 17~s based on a GPU-accelerated spectral-element wave
propagation solver which accommodates effects due to 3-D anelastic crust \& mantle structure, topography \& bathymetry, the ocean load, ellipticity, rotation, and self-gravitation.
We used an adjoint-state method to calculate Fr\'echet derivatives in 3D anelastic Earth models
facilitated by a parsimonious storage algorithm.
The simulations were performed on the Cray XK7 ``Titan'' and the IBM Power~9 ``Summit'' at the Oak Ridge Leadership Computing Facility.
We quantitatively evaluated GLAD-M25 by assessing misfit reductions and traveltime anomaly histograms in twelve measurement
categories.
We performed similar assessments for a held-out data set consisting of 360 earthquakes,
with results comparable to the actual inversion.
We highlight the new model for a variety of plumes and subduction zones.
\end{summary}

@@

Current global shear wavespeed models are in general agreement regardless of data type and inversion strategy in terms of long-wavelength heterogeneity \citep{ritzwollerlavely1995,TW01,beckerboschi2002}.
However, discrepancies between models become noticeable at shorter wavelengths.
Using accurate 3D simulations of seismic wave propagation and the computation of data sensitivities in 3D background models are key requirements for improving resolution in tomographic images on all scales~\citep{Tromp2020}.
Such detailed images are essential for understanding mantle dynamics and related surface tectonic processes
---for example the origin of hotspots and the driving mechanisms of plate motions and earthquakes.
Higher resolution wavespeed models are also important for accurately locating earthquakes, and are required from an engineering point of view to assess seismic hazard in earthquake prone regions and to detect and locate nuclear explosions.

With these goals in mind,
in this study we use a GPU-accelerated version of the 3D spectral-element solver
SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b} on the supercomputers ``Titan'' and ``Summit'' at the Oak Ridge Leadership Computing Facility (OLCF) for global adjoint tomography.
These simulations accommodate the full 3D complexity of global Earth models,
including 3D anelastic crust and mantle structure, self-gravitation, rotation, ellipticity, topography \& bathymetry, and the load of the oceans.
No compromises are made with regards to resolving the Earth's crust,
which is explicitly captured by the spectral-element mesh~\citep{tromp2010a},
thereby eschewing the need for ubiquitous ``crustal corrections''.
The ultimate goal is to use every single piece of information in seismograms,
a task made partly feasible based on the automated window selection tool FLEXWIN~\citep{maggi2009automated}.

Global adjoint tomography has a well-defined but complex workflow with multiple stages.
% including numerical simulations of synthetic seismograms (forward simulations) for all events,
% pre-processing of seismic data, making measurements, data assimilation, Fr\'echet derivative
% calculations (adjoint simulations), and post-processing of the gradient for quasi-Newton model
% updates.
It is essential to optimize, automate, and harden the entire process using workflow management tools, especially with large data sets.
For each iteration,
1,480 forward and adjoint simulations need to be performed (one pair for each earthquake in the database),
generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours.

This article is organized as follows.
Section~\ref{section:seismic data} illustrates the earthquakes and seismographic stations used in the inversion,
as well as the assimilated seismic data. 
Sections~\ref{section:misfit} and~\ref{section:parameterization} describe the misfit function minimized during the inversion process
and the related model parameterization.
Section~\ref{section:misfit_evolution} describes the evolution of the misfit, and in Section~\ref{section:evaluation} we evaluate the model based on point-spread function analyses and a held-out data set of 360 earthquakes.
Finally, in Section~\ref{section:model}
we compare the results of our inversion with global shear wavespeed models 
TX2015~\citep{TX2015} and SEMUCB-WM1~\citep{french2015broad},
as well as compressional wavespeed models GAP-P4~\citep{fukao2013subducted} and UU-P07~\citep{van2018atlas}.
We conclude with a discussion of future opportunities and directions.

\section{Seismic data}
\label{section:seismic data}

Fig.~\ref{fig:eventsstations}(a) shows a map of the 1,480 earthquakes
selected from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global}
and used in this study.
To ensure a good signal-to-noise ratio on a global scale,
the smallest moment magnitude in the database is set to~5.5,
thereby capturing more deep events,
and, to avoid complications associated with source dimension and directivity,
the largest moment magnitude is set to~7.2.
Prior to the structural inversion,
we performed source inversions using model GLAD-M15 and the CMT inversion algorithm of \cite{liu2004spectral},
as described in the Supplementary Online Material (SOM).

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/events_1480.pdf} \\
  \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
  \caption{\small{(a) Distribution of 1,480~earthquakes used in this study. The color of each beach ball reflects its depth range, where blue designates events shallower than 50~km, green events between 50~km and 300~km, and red events deeper than 300~km.
  (b) Distribution of the 11,800~seismographic stations used in this study. Colors denote the number of events for which a given station contributes waveforms to the structural inversion. Stations with a number of event responses $<400$ are plotted in smaller size; these are usually temporary arrays deployed over a short period of time, frequently ocean bottom seismometers. The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.
  \towenjie{Remove panels (b) and (c) and fix up the figure. Make sure the station count starts at 1, not 0.}
  }}
  \label{fig:eventsstations}
\end{figure}

The seismographic stations used in this study are plotted in Fig.~\ref{fig:eventsstations}(b) and
were selected to optimize global coverage
and high data quality.
In addition to the seismographic  stations used for the source inversions,
we included available data for our 1,480 event earthquake database from many data centers,
including IRIS, ORFEUS, INGV, IPGP, ETH, and GEONET.
Regional and temporary networks,
such as US Array~(TA),
Africa Array~(AF), the Canadian National Seismograph Network~(CN), Geoscience Australia~(AU),
the Antarctic Seismographic Argentinean Italian Network~(AI),
and the New Zealand National Seismograph Network~(NZ),
constitute a significant part
of our database and greatly improve coverage in certain regions.

To illustrate which seismic phases end up being assimilated,
Figs.~\ref{fig:window_density_Z}, \ref{fig:window_density_R}, and \ref{fig:window_density_T} show time-distance plots
for vertical, radial, and transverse component 17--40~s body waves,
respectively,
in which the Pyflex window count is used to identify parts of seismograms being assimilated.
The figures highlight all the well known body traveltime branches.
Collectively, the numerous compressional wave arrivals identified in Figs.~\ref{fig:window_density_Z} and~\ref{fig:window_density_R} are helpful to constrain the compressional wavespeed structure in the model.
The Pyflex window selection algorithm is currently configured not to pick body waves after the arrival of the surface waves, which is why the PcP and ScS branches are missing at shorter epicentral distances.
This is something we will reconsider in future applications by adjusting the FLEXWIN selection parameters, and perhaps also by introducing aspects of machine learning~\citep{chen2017}.
